Details of specific functions

### 2020-09-25 inst/gitbook/03_specific-tutorials.Rmd
Up gitbook

## Measuring the distance between the elements of the second group
## and the centroid of the first group
summary(dispRity(grouped_space, metric = point.dist,
                 between.groups = list(c(2,1)))))

>>>>

## Measuring the distance between the elements of the second group
## and the centroid of the first group
summary(dispRity(grouped_space, metric = point.dist,
                 between.groups = list(c(2,1))))
